Various examples of cdf plots

### 2015-11-05 analysis/plot_cdf_eg.Rmd
correct file directory

#df is a list with components method,seed, scenario
#cdf is evaluated at x
#returns list of x,y,pi0, where cdf values are in y
get_cdf = function(df,dsc=dsc_shrink,x=seq(-6,6,length=100),homedir="../output"){
  m=df$method
  if(m=="truth"){m="ash.n"}
  temp=load_example(dsc,df$seed,df$scenario,m,homedir)
  pi0=temp$meta$pi0

>>>>

#df is a list with components method,seed, scenario
#cdf is evaluated at x
#returns list of x,y,pi0, where cdf values are in y
get_cdf = function(df,dsc=dsc_shrink,x=seq(-6,6,length=100),homedir="../output/dsc-shrink-files"){
  m=df$method
  if(m=="truth"){m="ash.n"}
  temp=load_example(dsc,df$seed,df$scenario,m,homedir)
  pi0=temp$meta$pi0
